---
title: "NBA Data"
author: "Joe DiNoto"
date: "3/20/2021"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

First, load packages.

```{r message=FALSE,warning=FALSE,error=FALSE}
library(tidyverse)
library(ggplot2)
library(dplyr)
library(tidytuesdayR)
library(scales)
```

Second, grab the data.

```{r}
player_data <- read.csv("player_data.xls")
players <- read.csv("Players.xls")
seasons_stats <- read.csv("Seasons_Stats.csv")
```

Grab the player name, year, and team. 
```{r}
nba <- seasons_stats %>%
  select(Year, Player, Tm) %>%
  filter(!is.na(Year)) #remove NAs 
```

What are the range of years? 

```{r}
summary(nba$Year)
```

Which player stayed with a team the longest? (1950-2017)
```{r}
nba %>%
  count(Player,Tm, sort=TRUE) %>%
  head(20)
```

What is the distribution of how long a player stays with a team?

```{r}
nba %>%
  count(Player,Tm, sort=TRUE) %>%
  ggplot(aes(Player,n)) +
  geom_line()

```

Who played for the most teams?
```{r}
nba %>%
  count(Player,Tm)%>%
  count(Player, sort=TRUE) %>%
  head(20)
```
There were three (3) George Johnsons in the NBA.
```{r}
player_data %>%
  filter(name=="George Johnson")
```

Which means Tony Massenburg is the player who has played on the most teams (14). 
```{r}
player_data %>%
  filter(name == "Tony Massenburg")
```

Which 14 teams did he play for? 
```{r}
nba %>% 
  filter(Player=="Tony Massenburg") %>%
  count(Tm, sort=TRUE)
```

